Observed vs. Simulated Year Comparison

### 2021-12-11 03-post-process/compare-sim-to-obs.Rmd
Include calculation of aggregate quantities in sim vs. obs RMD

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario:', params$scenario)`"
output: html_document
params:
  scenario:
    label: "Scenario"
    value: "base-with-sim-medium"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
output: html_document
params:
  scenario:
    label: "Scenario"
    value: "base-with-sim-medium"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

```{r add-nor-lgr-smolt-aggregate}
# extract smolt at LGR
Ma = post_subset(post, "^Ma[", matrix = TRUE)

# for each posterior sample, calculate the total aggregate return
out_nor = out_hor = NULL
for (i in 1:nrow(Ma)) {
  Ma_i = array_format(Ma[i,])
  nor = Ma_i[,1,1,] + Ra_i[,2,1,]
  hor = Ra_i[,2,2,]

  out_nor = rbind(out_nor, rowSums(nor))
  out_hor = rbind(out_hor, rowSums(hor))
}

# build the indices for each element: the year
r_ind = 1:nrow(nor)

# make element names
colnames(out_nor) = paste0("Ma_aggregate[", r_ind, ",", "1", "]")
colnames(out_hor) = paste0("Ma_aggregate[", r_ind, ",", "2", "]")
out = cbind(out_nor, out_hor)

```{r add-Ra-aggregate}
# extract spawners returning to tributary
Ra = post_subset(post, "^Ra[", matrix = TRUE)

# for each posterior sample, calculate the total aggregate return
out_nor = out_hor = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])
  nor = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
  hor = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]
  tot = nor + hor

  out_nor = rbind(out_nor, rowSums(nor))
  out_hor = rbind(out_hor, rowSums(hor))
}

# build the indices for each element: the year
r_ind = 1:nrow(nor)

# make element names
colnames(out_nor) = paste0("Ra_aggregate[", r_ind, ",", "1", "]")
colnames(out_hor) = paste0("Ra_aggregate[", r_ind, ",", "2", "]")
out = cbind(out_nor, out_hor)
